---
title: "Traditional Medicine Industry in Indonesia"
author: "Nathasya Pramudita"
date: "2023-08-01"
output: github_document
---

```{r include=FALSE}
library(tidyverse)
library(ggrepel)
library(readxl)

# Import dataset
total_industry <- read_excel("~/Datasets/Product_obat_tradisional/jumlah_industri_berdasarkan_prov.xlsx")
total_registered <- read_excel("~/Datasets/Product_obat_tradisional/jumlah_pendaftar_berdasarkan_prov.xlsx")
catagories_industry <- read_excel("~/Datasets/Product_obat_tradisional/jenis_dan_jumlah_industri.xlsx")
total_product_by_categories <-read_excel("~/Datasets/Product_obat_tradisional/jumlah_produk_berdasarkan_kategori.xlsx")
percentage_import_export <- read_excel("~/Datasets/Product_obat_tradisional/persentase_import_export.xlsx")

# join two tables into one
total_industry_and_registered <- total_industry %>%
  full_join(total_registered, by=c("provinsi", "id_provinsi", "Pulau"))

# remove the two dataset that already merged
rm(total_industry, total_registered)
# remove some variables
percentage_import_export <-percentage_import_export %>%
  select(-total_seluruh)

# rename variables
total_industry_and_registered <- total_industry_and_registered %>%
  rename("pulau" = Pulau)

# created new variable from percentage_import_export
percentage_import_export$percentage <- percentage_import_export$total_produk / sum(percentage_import_export$total_produk)
```

----

# About dataset

This dataset is came from [portal satu data BPOM](https://satudata.pom.go.id/datasets).
It's an open source dataset from Indonesia government in Foods and Drugs administration sector. The data is from *2021-10-01*.

My focus of this project is finding important key about **Traditional Medicine Industries in Indonesia**. The dataset is about:

|Data Frame|Information|
|----|----|
|total_industry_and_registrant|Consist of 31 observant and 5 variables. It's about total and how much industries that want to register as Traditional Medicine manufacturer by Province in Indonesia|
|categories_industry|3 observant and 2 variables. Consist of the type of industry and total of each type of that industry|
|total_prouct_by_categories|3 observant and 2 variables. Consist of the categories of product and total of each product|
|percentage_import_export|With 3 observant and 3 variables that consist of total product of export and import, and percentage each sale|

# Total registrant and Industry of Traditional Medicine in Indonesia

```{r Number of Registrant Manufacture, warning=FALSE}
# Number of Registrant Manufacture of Traditional Medicine in Indonesia

total_industry_and_registered %>%
  ggplot(aes(x=provinsi, y=jumlah_pendaftar, color=pulau, label=provinsi))+
  geom_point()+
  labs(title="Number of Traditional Medicine Product Registrar by Province",
       caption = "Source data: Portal Satu Data BPOM",
       x="",
       y="Total Industry",
       fill="Pulau: ")+
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank())+
  geom_text_repel(size=3)+
  theme(legend.position="bottom")

```

```{r total_manufacture_operational, warning=F}
# Total Number Traditional Medicine Factory in Indonesia
total_industry_and_registered %>%
  ggplot(aes(x=provinsi, y=jumlah_industri, color=pulau, label=provinsi))+
  geom_point()+
  labs(title="Total Industry of Traditional Medicine in Indonesia",
       caption = "Source data: Portal Satu Data BPOM",
       x="",
       y="Total Industry")+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  geom_text_repel(size=3)+
  theme(legend.position="bottom")
```

# Percentage of Import, Export, and Local production of Traditional Medicine in Indonesia

```{r pie chart for percentage_import_export, warning=F}
percentage_import_export %>%
  ggplot(aes(x="", percentage, fill=product_type))+
  geom_bar(stat="identity", color="white")+
  coord_polar("y", start=0)+
  geom_text(aes(label=paste0(round(percentage*100), "%")),
            position=position_stack(vjust=0.5))+
  labs(title="Percentage of Traditional Medicine Industry by Market")+
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank())+
  scale_fill_brewer(palette = "green", name = "Producing For")

```

# Categories of Traditional Medicine in Indonesia

```{r pie chart for categories_industry, warning=F}
catagories_industry %>%
  ggplot(aes(jenis_industri, jumlah_industri, fill=jenis_industri))+
  geom_col()+
  labs(title="Categories of Traditional Medicine Industry",
       subtitle = "Based on Industries Type",
       caption="Source: Portal Satu Data BPOM",
       x="Industry Type",
       y= "Total Industry",
       fill="Industry Categoriest: ")+
  theme(legend.position = "bottom")+
  scale_fill_brewer(palette="PuBu")+
  theme_linedraw()

```

Information table `Catagories of Traditional Medicine Industry Based on Industry Type`:

* IOT = Industri Obat Tradisional
* UKOT = Usaha Kecil Obat Tradisional
* UMOT = Usaha Mikro Obat Tradisional

# Traditional Medicine by Categories of Product

```{r Categories_of_product, warning=F}
total_product_by_categories %>%
  mutate("percentage_cat" = jumlah_produk / sum(jumlah_produk)) %>%
  ggplot(aes(kategori_produk, percentage_cat, fill=kategori_produk))+
  geom_col()+
  labs(title="Traditional Medicine by Categories of Product",
       x="Categories of Product",
       y="Percentage",
       fill="Categories 0f Product")+
  theme(legend.position = "bottom")+
  scale_fill_brewer(palette="OrRd")+
  theme_gray()

```

---